Sparse Function-space Representation \\ of Neural Networks

### 2023-05-19 paper/main.tex
added hyperparams for CL experiments

\begin{table}[t!] 
  \centering\scriptsize
  \caption{Negative log predictive density (NLPD) (lower better) for SVGP (sparse GP mean and variance), SVGP NN (NN mean and sparse GP variance), GP subset (subset GP mean and variance) and GP NN subset (NN mean and GP subset variance) for inducing points in $[16, 32, 64, 128, 256]$. } 
	\label{tbl:uci-appendix}
	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{2pt}
	\setlength{\tblw}{0.14\textwidth}

@@

>>>>

\begin{table}[t!] 
  \centering\scriptsize
  \caption{Negative log predictive density (NLPD) (lower better) for SVGP (sparse GP mean and variance), SVGP NN (NN mean and sparse GP variance), GP subset (subset GP mean and variance) and GP NN subset (NN mean and GP subset variance) for inducing points in $[16, 32, 64, 128, 256]$. } 
	\label{tbl:uci-appendix}
	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{2pt}
	\setlength{\tblw}{0.2\textwidth}

@@

The results reported in \cref{tbl:cl_table_1}, are obtained using the following hyperparameters:

%% Hyperparms used in the different experiments:
\textbf{S-MNIST (40 pts./task):}
\begin{itemize}
	\item[-] Online-EWC: SGD with learning rate $0.03$, batch size  10, number of epochs 1, $\lambda=90$, $\gamma=1.0$.
	\item[-] SI: SGD with learning rate 0.1, batch size 10, number of epochs 1, $c=1.0$, $\xi=0.9$.
	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
	\item[-] DER: SGD with learning rate 0.03, batch size 10, buffer batch size 10, number epochs 1, $\alpha=0.3$, reservoir buffer size 200.
	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 10.
	\item[-] SFR: Adam with learning rate 0.0003, batch size=32, $\tau=1$, $\delta=0.0001$,  number of epochs 1.
\end{itemize}

\textbf{S-MNIST (200 pts./task):}
\begin{itemize}
	\item[-] Online-EWC: SGD with learning rate $0.03$, batch size  10, number of epochs 1, $\lambda=90$, $\gamma=1.0$.
	\item[-] SI: SGD with learning rate 0.1, batch size 10, number of epochs 1, $c=1.0$, $\xi=0.9$.
	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
	\item[-] DER: SGD with learning rate 0.03, batch size 10, buffer batch size 10, number epochs 1, $\alpha$ 0.2, reservoir buffer size 1000.
	\item[-] FROMP: Adam, learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 80.
	\item[-] SFR: Adam learning rate 0.0001, batch size=32, $\tau=0.5$, $\delta=1 \cdot 10^{-5}$, number of epochs=5.
\end{itemize}

%% Placeholders for now
\textbf{S-FMNIST (200 pts./task):}
\begin{itemize}
	\item[-] Online-EWC: SGD with learning rate $0.03$, batch size  10, number of epochs 5, $\lambda=90$, $\gamma=1.0$.
	\item[-] SI: SGD with learning rate 0.1, batch size 10, number of epochs 5, $c=1.0$, $\xi=0.9$.
	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
	\item[-] DER: SGD with learning rate 0.03, batch size 10, buffer batch size 10, number epochs 5, $\alpha$ 0.2, reservoir buffer size 200.
	\item[-] FROMP: Adam with learning rate $1 \cdot 10^{-4}$, batch size 32, number of epochs 10, $\tau = 10$, random selection for memorable points.
	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 60.
	\item[-] SFR: Adam, learning rate=0.0003, batch size=32, $\tau=1.0$, $\delta=0.0001$, number of epochs=5.
\end{itemize}

\textbf{P-MNIST (200 pts./task):}
\begin{itemize}
	\item[-] Online-EWC: SGD with learning rate $0.1$, batch size 128, number of epochs 10, $\lambda=0.7$, $\gamma=1.0$.
	\item[-] SI: SGD with learning rate 0.1, batch size 138, number of epochs 10, $c=0.5$, $\xi=1.0$. 
	\item[-] VCL (with coresets): Adam, learning rate 0.001, batch size 256, number of epochs 100, selection method for coresets random choice.
	\item[-] DER:  SGD with learning rate 0.01, batch size 128, buffer batch size 128, number epochs 10, $\alpha=0.3$, reservoir buffer size 2000.
	\item[-] FROMP: Adam with learning rate $1 \cdot 10^{-3}$, batch size 128, number of epochs 10, $\tau = 0.5$, lambda descend selection for memorable points.
	\item[-] S-FSVI: Adam, learning rate $5 \cdot 10^{-4}$, batch size 128, number of epochs 10.
	\item[-] SFR: Adam learning 0.0003, batch size=64, $\tau=1.0$, $\delta=0.0001$. 
\end{itemize}

In addition the ablation experiments for SFR, we used the same hyperparameters reported for the full approach.
